### 2017-10-25 Draft2/Appending.Dynamic.tex
Renaming

@@

From \ref{lem:CapacitySequence} I know the exact capacities $\VarList$ takes on as $n$ items are appended. Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated. Then the total length of arrays allocated is

>>>>

\begin{lemma}
\label{lem:CapacitySeq}
	Let $\VarList$ by a dynamic array. Let its \textbf{capacity sequence}, $\VarCapacitySeq$, be the capacities $\VarList$ takes on as $n$ items are appended. Then

	$$
	\VarCapacitySeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
	$$
\end{lemma}

@@

From \ref{lem:CapacitySeq} I know the exact capacities $\VarList$ takes on as $n$ items are appended. Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated. Then the total length of arrays allocated is

### 2017-10-25 Draft2/Appending.Growth.tex
Take care of Section 3
Renaming

\ref{lem:CapacitySequence} still holds, since all of the assumptions made there are also true for growth arrays. In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:

@@

I now approximate this expression using $\TextTilde$. First, I approximate $k$ using big-O:

@@

Now, the $k$-term disappears when using $\TextTilde$ to approximate $\FuncWritesNew(n)$, leaving just $n$:

\begin{align*}
\FuncWritesNew(n) &\TextTilde n + \FuncWrites(k)\\
&= n + O(\log n)\\
&\TextTilde n
\end{align*}

@@

\begin{align*}
\FuncSpaceNew(n) \TextTilde 2^{\lceil \log_2 n \rceil} = O(n)
\end{align*}

>>>>

\ref{lem:CapacitySeq} still holds, since all of the assumptions made there are also true for growth arrays. In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:

@@

I now approximate this expression using $\sim$. First, I approximate $k$ using big-O:

@@

Now, the $k$-term disappears when using $\sim$ to approximate $\FuncWritesNew(n)$, leaving just $n$:

\begin{align*}
\FuncWritesNew(n) &\sim n + \FuncWrites(k)\\
&= n + O(\log n)\\
&\sim n
\end{align*}

@@

\begin{align*}
\FuncSpaceNew(n) \sim 2^{\lceil \log_2 n \rceil} = O(n)
\end{align*}
